Dantzig Selector Applied on mm-Wave MIMO Channel Estimation and and Error Analysis

### 2021-06-08 article/main.tex
Use round brackets for functions

For simplicity we suppose uniform linear arrays, for which the response would be,
%
\Disp {
\V {a} \SB {\psi', N}
= \frac {1} {\R {N}} \sum_{n_h=0}^{N-1} \mathsf {e} ^{\mathsf {i} n_h \psi'} \V {u} _{n_h}
\in \mathbb {C} ^ {N} 
}

And consider the virtual representation of the MIMO channel, \cite {ALS14},
%
\Disp {
\M {H}
=\sum_{l=0} ^{L-1}
\a_l
\V {a} \SB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \f_l', N_{H,r}}
\V {a} \SB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \th_l', N_{H,t}}^\dagger 
}
%
The physical meaning of \m {\f_l'} is the \m {l}-th angle of incidence of departure electronic wave, and \m {\th_l'}, the \m {l}-th angle of arrival wave, and \m {d_{\mathrm {arr}}} is the distance between two adjacent antennae.

@@

We consider hybrid beamforming at both the transmitter and receiver ends, as shown in Figure 2.
Each end consists of both digital and analog precoders and combiners.
In the transmitter end, there are (seeing towards the receiver end), the digital precoder \m {\M {F} _B \in \mathbb {C} ^{N_B \D N_B}} and the analog precoder \m {\M {F} _R \in \mathbb {C} ^{N_{H,t} \D N_B}}.
Similarly, in the receiver end, there are (seeing towards the transmitter end) the digital combiner \m {\M {W} _B \in \mathbb {C} ^{N_B \D N_B}} and the analog combiner \m {\M {W} _R \in \mathbb {C} ^{N_B \D N_{H,r}}}.
Recall that analog precoders may only have values of unity magnitude.
%
\Disp {
\Nm {\RB {\M {F} _R} _{\SB {n_H, n_{R,t}}}}
= &1, \\
%
\Nm {\RB {\M {W} _R} _{\SB {n_{R,r}, n_H}}}
= &1,
}
%
where we assume \m {N_{H,t}, N_{H,r} \gg N_B}.

Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \mathbb {C} ^{N_B \D N_B}} with each entry being i.i.d.\ standard normal.
Let us introduce the effective channel
%
\Disp {
\M {Y}
:=\M {W} _B \M {W} _R \RB {\M {H} \M {F} _R \M {F} _B +\M {Z}} 
}
%
Our task then amounts to recovering \m {\M {H}}, and generating \m {\M {W} _R}, \m {\M {W} _B}, \m {\M {F} _R}, and \m {\M {F} _B}.

@@

Let vec stand for vectorization of matrices along each column, and \m {\otimes} for Kronecker product.
Then it is more appealing to write
\Disp {
\V {h}
:= &\mathrm {vec} \SB {\M {H}} \\
\V {y}
:= &\mathrm {vec} \SB {\M {Y}} \\
\V {z}
:= &\mathrm {vec} \SB {\M {W} _B \M {W} _R \M {Z}} \\
\M {Q}
:= &\RB {\M {F} _B^\intercal \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R} \\
}
to formulate the problem as a linear system:
\Disp {
\V {y}
=\M {Q} \V {h} +\V {z} 
}

At this stage, it is not obvious that \m {\V {h}} must be sparse, so we apply discrete Fourier transform matrix \m {\M {K}} on both sides.
Indeed, if we write
\Disp {
\M {G}
=\M {K}^\dagger _r \M {H} \M {K} _t
}
then
\Disp {
\M {Y}
=\M {W} _B \M {W} _R \M {K} _r \D \M {G} \D \M {K}^\dagger _t \M {F} _R \M {F} _B
+\M {W} _B \M {W} _R \M {Z}
}
Now, set for brevity
\Disp {
\M {P}
:=\RB {\M {F} _B^\intercal \M {F} _R^\intercal \M {K}^\ast _t} \otimes \RB {\M {W} _B \M {W} _R \M {K} _r}
}
and
\Disp {
\V {g}
:= \mathrm {vec} \SB {\M {G}}
}
accordingly
\Disp {
\V {y}
=\M {P} \V {g} +\V {z} 
}

In short, our plan becomes

\begin {itemize}
\item Let \m {\g_{\mathrm {DS}} \geq 0} be given.
\item Input \m {\M {F} _B \in \mathbb {C} ^{N_R \D N_B}},
\m {\M {F} _R \in \mathbb {C} ^{N_{H,t} \D N_R}},
\m {\M {W} _R \in \mathbb {C} ^{N_R \D N_{H,r}}},
\m {\M {W} _B \in \mathbb {C} ^{N_B \D N_R}},
and \m {\M {Y} \in \mathbb {C} ^{N_B \D N_B}}.
\item Find \m {\M {P} \in \mathbb {C} ^{N_B ^2 \D N_{H,t} N_{H,r}}}, \m {\V {y} \in \mathbb {C} ^{N_B ^2}} as in above.
\item Compute the convex program
\Disp {
\hat {\V {g}}
\leftarrow \begin {cases}
\Min {\V {g}' \in \mathbb {C} ^{N_{H,t} N_{H,r}}} & \VNm {\V {g}'} _1 \\
\mathrm {subject} \; \mathrm {to} \quad & \VNm {\M {P}^\dagger \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g_{\mathrm {DS}} \\
\end {cases} 
}
\item Convert \m {\hat {\V {g}}} back to the space domain, namely
\Disp {
\hat {\M {G}}
\leftarrow \mathrm {vec}^{-1} \SB {\hat {\V {g}}} 
}
\item Recover the estimated \m {\hat {\M {H}}}, as
\Disp {
\hat {\M {H}}
\leftarrow \M {K} _r \hat {\M {G}} \M {K}^\dagger _t
}
\item Output \m {\hat {\M {H}}}.
\end {itemize}

@@

To simplify expressions, define
%
\Disp {
\f_l
= &2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \f_l'
  \; \mathrm {mod}\; \RB {2\pi} \\
%
\th_l
= &2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \th_l'
  \; \mathrm {mod}\; \RB {2\pi} 
}

\textbf {Proposition 1}
Let \m {\f} be given.
Then, for any random instance of \m {\f},
%
\Disp {
\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
\leq \frac {2} {\pi} \log N 
}

To show this, introduce
\Disp {
\psi \SB {\f, n_H}
:=\RB {
   \f \; \mathrm {Mod}\; \frac {2\pi} {N}
   + \RB {\frac {2 n_H} {N} + 1} \pi
} \;
\mathrm {mod}\; \RB {2\pi}
- \pi 
}
Also define
\Disp {
\Nm {D \SB {\psi'}}
:= &\frac {\Nm {\sin \SB {N \psi'/2}}} {\Nm {\sin \SB {\psi' /2}}} \\
\leq &B \SB {\psi'}
:= \frac {48} {\Nm {\psi'^2 -24} \Nm {\psi'}}, \\
}
Then,
\Disp {
\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
\leq \frac {1} {N}
\VNm {
\RB {
   \sum_{n_H' =0}^{N -1}
      B \SB {\psi \SB {\f, n_H'}}
      \V {u} _{n_H'}
} _{\SB{\mathcal {C}}}
} _1
}
Or, if we drop \m {s},
\Disp {
\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
\leq &\frac {1} {N} \D \frac {N} {2\pi} \D 2 \int_{\pi s/N}^{\pi} B \SB {\psi'} ^2 d \psi' \\
= &\frac {48} {N \pi^3}
\int _{s /N} ^1 \frac {1} {\RB {24/\pi^2 -x'^2} ^2 x'^2} dx' \\
\leq &\frac {2} {\pi} \log N 
}

\textbf {Proposition 2}
The bound
\Disp {
\VNm {\M {g} _{\SB{\mathcal {C}}}} _1
\leq \frac {1} {3} L \RB {\log N_{H,t} + \log N_{H,r}} ^2
}
holds for probability \m {p}, with
\Disp {
1 -p
\leq 2 \exp \SB {- \frac {9L} {\pi}} 
}
This is proved by using Proposition 1 with triangle inequality, and bound the sample mean by Hoeffding inequality.

@@

Nevertheless, notice that if angles \m {\th_l} (respectively \m {\f_l}) are exactly the multiples of \m {2 \pi / N_{H,t}} (respectively \m {2 \pi / N_{H,r}}), then for some \m {S}-sparse \m {\V {d}'} and unitary \m {\M {U}},
\Disp {
&\VNm {\M {W} _B \M {W} _R \M {H} \M {F} _R \M {F} _B} _2 \notag \\
= &\VNm {
   \M {W} _B \M {W} _R \M {K} _r \M {U} \D
   \mathrm {diag} \SB {\mathrm {abs} \SB {\V {d}'}} \D
   \M {U} ^\dagger \M {K} _t ^\dagger \M {F} _R \M {F} _B} _2 \notag \\
= &\VNm {
   \M {W} _B \M {W} _R \M {K} _r \M {U}
   \R {\mathrm {abs} \SB {\V {d}'}}} _2 \D
   \VNm {\M {F} _B ^\dagger \M {F} _R ^\dagger \M {K} _t \M {U}
   \R {\mathrm {abs} \SB {\V {d}'}}} _2 \notag \\
\eqsim &\VNm {\M {G}} _2 \RB {1 +2\d_s} 
}
Thus, even we cannot make sure that \m {\M {P}} is \m {\d_s} RIP with respect to all possible \m {\V {g}}'s, at least \m {\M {P}} has RIP with respect to relevant values of \m {\V {g}}.

@@

Finally, we shall show the proposed bound.
For simplicity, set \m {S = Ls^2}, thus \m {S =L \log N_h}.
And, for concreteness, suppose \m {\d_S \leq \frac {1} {8}}.

\textbf {Theorem 9}
Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as above.
Then it holds that
\Disp {
\VNm {\V {d}} _2
\eqsim \mathcal {O} \SB {\R {L} \R {\log N_h}^3} 
}
for probability \m {p}, with
\Disp {
1 -p
\eqsim \mathcal {O} \SB {\mathsf {e} ^{-N_R \R {\d_s} /4}} 
}

To show this, by the definition of truncation, by \m {\ell_p} norm inequality, by Proposition 6,
\Disp {
\VNm {\M {P} _{\SB {\mathcal {AB}}}^\intercal \M {P} \V {d}} _2
\leq &\VNm {\M {P}^\intercal \M {P} \V {d}} _2 \notag \\
\leq &\R {S} \VNm {\M {P}^\intercal \M {P} \V {d}} _\infty \notag \\
\leq &2.83 \R {L} \log N_h
}
By \m {\ell_p}-norm inequality, by the definition of truncation, by Proposition 8, and by above,
\Disp {
\VNm {\V {d} _{\SB{\mathcal {A}}}} _1
\leq &\R {S} \VNm {\V {d} _{\SB{\mathcal {A}}}} _2 \notag \\
\leq &\R {S} \VNm {\V {d} _{\SB{\mathcal {AB}}}} _2 \notag \\
\leq &3.44 L \R {\log N_h}^3
+0.262 \VNm {\V {d} _{\SB{\mathcal {C}}}} _1
}
Then, substituting this and Proposition 2 above into Proposition 5, we get
\Disp {
\VNm {\V {d} _{\SB{\mathcal {C}}}} _1
\leq 5.12 L \RB {\log N_h}^2
}
Now Proposition 8 becomes
\Disp {
\VNm {\V {d} _{\SB{\mathcal {AB}}}} _2
\leq 3.44 \R {L} \log N_h + 1.35 \R {L} \R {\log N_h} ^3
}
Finally, by plugging \m {\VNm {\V {d} _{\SB{\mathcal {AB}}}} _2} and \m {\VNm {\V {d} _{\SB{\mathcal {C}}}} _1} into Proposition 7, we get
\Disp {
\VNm {\V {d}} _2
\leq 4.79 \R {L} \R {\log N_h}^3
}
Therefore, we set \m {\chi = \R {L} \R {\log N_h}^3}, so that \m {\VNm {\V {d}} _2 = \mathcal {O} \RB {\chi}}, as claimed.
The failure probability is taken from Proposition 3.

@@

First, complex numbers have to be recorded as the real and imaginary parts, to speed up calculation.
Let \m {\mathcal {R}} denote the representation of complex vectors and matrices by real vectors and matrices.
With definitions \m {\tilde {\V {y}} = \mathcal {R} \SB {\V {y}}},
\m {\tilde {\V {g}} = \mathcal {R} \SB {\V {g}}},
\m {\tilde {\M {P}} = \mathcal {R} \SB {\M {P}}},
\m {\tilde {\V {z}} = \mathcal {R} \SB {\V {z}}},
we have by construction
%
\Disp {
\V {\tilde {y}}
= \M {\tilde {P}} \V {\tilde {g}} +\V {\tilde {z}} 
}

@@

Alternatively, in our investigation, we cast DS into a basis pursuit denoising form, for suitable \m {\l} \cite {BoV04} as below.

\Disp {
\Hat {\V {g}}
\leftarrow \Min {\V {g}' \in \mathbb {C} ^{N_{H,t} N_{H,r}}}
\RB {\VNm {\V {g}'} _1 + \l \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty}
}

However, there is no simple way to determine the value of \m {\l} in advance.
We have tried \m {\l = N_{H,t} N_{H,r} / \g_{\mathrm {DS}}} in the simulation.

@@

We discuss the complexity of DS, Lasso, and OMP.
For DS, suppose a linear program has an \m {N} dimensional variable and \m {M} inequality constraints, then its complexity is \m {\mathcal {O} \SB {N^2 M}}, assuming the Dantzig simplex method is used \cite {BoV04}.
For our case, that would be \m {\mathcal {O} \SB {4 N_h ^2 \D 8 N_h} = \mathcal {O} \SB {N_h ^3}}.

Alternatively, suppose Newton method is used.
Here, we have self-concordance for linear program \cite {BoV04}.
Let \m {\V {g} _0} denote the starting value of \m {\V {g}'}, and \m {\V {g} ^{\star}} the the point of convergence.
Then the number of Newton steps, which we take to be the complexity, is bounded by \cite {BoV04}
\Disp {
C_{\mathrm {Newton}}
\propto \RB {\VNm {\V {g}_0 -\V {g} ^{\star}}_1
+ \log_2 \log_2 \frac {1} {\e}}
}

Assume that, at the start the iteration, the Moore–Penrose inverse is close to the initial value of \m {\V {g}_0}, namely
%
\Disp {
\V {g}_0
=\V {g}_{\mathrm {LS}}
= \RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {y} 
}
And suppose that, in view of restricted isometry, \m {\M {P}} has unity-normed, almost orthogonal columns, so that
\m {\M {P} ^\dagger \M {P} \approx I _{N_h}}
Moreover, assume that \m {\V {g} ^\star \approx \V {g}}.
Then we simply have
\Disp {
C_{\mathrm {DS}}
=\mathcal {O} \SB {N_h ^3} 
}

For OMP \cite {TrG07}, \m {C_{\mathrm {OMP}} =\mathcal {O} \SB {L \RB {\log N_h} ^2}}.

For Lasso, it is equivalent to a quadratically constrained quadratic program, and there is not always a closed form for its complexity.
However, Lasso and DS are equivalent in certain conditions \cite {AsR10}, and we may suppose here they have the same complexity.
Alternatively, an argument similar to the above one for DS is valid for Lasso.
Therefore we take \m {C_{\mathrm {Lasso}} =\mathcal {O} \SB {N_h ^3}}.

@@

\begin{thebibliography}{30}
\bibitem{RSM13}
T. S. Rappaport, S. Sun, R. Mayzus, H. Zhao, Y. Azar, K. Wang, G. N. Wong, J. K. Schulz, M. Samimi, and F. Gutierrez, “Millimeter wave mobile communications for 5g cellular: It will work!” \textit {IEEE access}, vol. 1, pp. 335–349, 2013.

\bibitem{RDD18}
M. Rani, S. B. Dhok, and R. Deshmukh, “A systematic review of compressive sensing: Concepts, implementations and applications,” \textit {IEEE Access}, vol. 6, pp. 4875–4894, 2018.

\bibitem{CaT05}
E. J. Candès and T. Tao, “Decoding by linear programming,” \textit {IEEE Transactions on Information Theory}, vol. 51, no. 12, p. 4203, 2005.

\bibitem{CaT07}
E. Candès and T. Tao, “The dantzig selector: Statistical estimation when p is much larger than n,” \textit {The annals of Statistics}, vol. 35, no. 6, pp. 2313–2351, 2007.

\bibitem{BDD08}
[6] R. Baraniuk, M. Davenport, R. DeVore, and M. Wakin, “A simple proof of the restricted isometry property for random matrices,” \textit {Constructive Approximation}, vol. 28, no. 3, pp. 253–263, 2008.

\bibitem{BHS10}
W. U. Bajwa, J. Haupt, A. M. Sayeed, and R. Nowak, “Compressed channel sensing: A new approach to estimating sparse multipath channels,” \textit {Proceedings of the IEEE}, vol. 98, no. 6, pp. 1058–1076, 2010.

>>>>

We use an underline like \m {\V {v}} for vectors, two underlines like \m {\M {M}} for matrices.
A dagger \m {\dagger} stands for Hermitian, and \m {\intercal} for transpose.
A subscript with brackets like \m {\M {M} _{\SB{1,2}}} is its corresponding entry.

For simplicity we suppose uniform linear arrays, for which the response would be,
\Disp {
\V {a} \RB {\psi', N}
= \frac {1} {\R {N}} \sum_{n_h=0}^{N-1} \mathsf {e} ^{\mathsf {i} n_h \psi'} \V {u} _{n_h}
\in \mathbb {C} ^ {N} 
}
And consider the virtual representation of the MIMO channel, \cite {ALS14},
\Disp {
\M {H}
=\sum_{l=0} ^{L-1}
\a_l
\V {a} \RB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \f_l', N_{H,r}}
\V {a} \RB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \th_l', N_{H,t}}^\dagger 
}
The physical meaning of \m {\f_l'} is the \m {l}-th angle of incidence of departure electronic wave, and \m {\th_l'}, the \m {l}-th angle of arrival wave, and \m {d_{\mathrm {arr}}} is the distance between two adjacent antennae.

@@

We consider hybrid beamforming at both the transmitter and receiver ends, as shown in Figure 2.
Each end consists of both digital and analog precoders and combiners.
In the transmitter end, there are (seeing towards the receiver end), the digital precoder \m {\M {F} _B \in \mathbb {C} ^{N_B \D N_B}} and the analog precoder \m {\M {F} _R \in \mathbb {C} ^{N_{H,t} \D N_B}}.
Similarly, in the receiver end, there are (seeing towards the transmitter end) the digital combiner \m {\M {W} _B \in \mathbb {C} ^{N_B \D N_B}} and the analog combiner \m {\M {W} _R \in \mathbb {C} ^{N_B \D N_{H,r}}}.
Recall that analog precoders may only have values of unity magnitude.
\Disp {
\Nm {\RB {\M {F} _R} _{\SB {n_H, n_{R,t}}}}
= &1, \\
\Nm {\RB {\M {W} _R} _{\SB {n_{R,r}, n_H}}}
= &1,
}
where we assume \m {N_{H,t}, N_{H,r} \gg N_B}.

Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \mathbb {C} ^{N_B \D N_B}} with each entry being i.i.d.\ standard normal.
Let us introduce the effective channel
\Disp {
\M {Y}
:=\M {W} _B \M {W} _R \RB {\M {H} \M {F} _R \M {F} _B +\M {Z}} 
}
Our task then amounts to recovering \m {\M {H}}, and generating \m {\M {W} _R}, \m {\M {W} _B}, \m {\M {F} _R}, and \m {\M {F} _B}.

@@

Let vec stand for vectorization of matrices along each column, and \m {\otimes} for Kronecker product.
Then it is more appealing to write
\Disp {
\V {h}
:= &\mathrm {vec} \RB {\M {H}} \\
\V {y}
:= &\mathrm {vec} \RB {\M {Y}} \\
\V {z}
:= &\mathrm {vec} \RB {\M {W} _B \M {W} _R \M {Z}} \\
\M {Q}
:= &\RB {\M {F} _B^\intercal \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R} \\
}
to formulate the problem as a linear system:
\Disp {
\V {y}
=\M {Q} \V {h} +\V {z} 
}

At this stage, it is not obvious that \m {\V {h}} must be sparse, so we apply discrete Fourier transform matrix \m {\M {K}} on both sides.
Indeed, if we write
\Disp {
\M {G}
=\M {K}^\dagger _r \M {H} \M {K} _t
}
then
\Disp {
\M {Y}
=\M {W} _B \M {W} _R \M {K} _r \D \M {G} \D \M {K}^\dagger _t \M {F} _R \M {F} _B
+\M {W} _B \M {W} _R \M {Z}
}
Now, set
\Disp {
\M {P}
:= &\RB {\M {F} _B^\intercal \M {F} _R^\intercal \M {K}^\ast _t} \otimes \RB {\M {W} _B \M {W} _R \M {K} _r} \\
\V {g}
:= &\mathrm {vec} \RB {\M {G}}
}
Accordingly
\Disp {
\V {y}
=\M {P} \V {g} +\V {z} 
}

In short, our algorithm can be summarized more succinctly as below.
\begin {itemize}
\item Let \m {\g_{\mathrm {DS}} \geq 0} be given.
\item Input \m {\M {F} _B \in \mathbb {C} ^{N_R \D N_B}},
\m {\M {F} _R \in \mathbb {C} ^{N_{H,t} \D N_R}},
\m {\M {W} _R \in \mathbb {C} ^{N_R \D N_{H,r}}},
\m {\M {W} _B \in \mathbb {C} ^{N_B \D N_R}},
and \m {\M {Y} \in \mathbb {C} ^{N_B \D N_B}}.
\item Find \m {\M {P} \in \mathbb {C} ^{N_B ^2 \D N_{H,t} N_{H,r}}}, \m {\V {y} \in \mathbb {C} ^{N_B ^2}} as in above.
\item Compute the convex program
\Disp {
\hat {\V {g}}
\leftarrow \begin {cases}
\Min {\V {g}' \in \mathbb {C} ^{N_{H,t} N_{H,r}}} & \VNm {\V {g}'} _1 \\
\mathrm {subject} \; \mathrm {to} \quad & \VNm {\M {P}^\dagger \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g_{\mathrm {DS}} \\
\end {cases} 
}
\item Convert \m {\hat {\V {g}}} back to the space domain, namely
\Disp {
\hat {\M {G}}
\leftarrow \mathrm {vec}^{-1} \RB {\hat {\V {g}}} 
}
\item Recover the estimated \m {\hat {\M {H}}}, as
\Disp {
\hat {\M {H}}
\leftarrow \M {K} _r \hat {\M {G}} \M {K}^\dagger _t
}
\item Output \m {\hat {\M {H}}}.
\end {itemize}

@@

To simplify expressions, define
\Disp {
\f_l
= &2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \f_l'
  \; \mathrm {mod}\; \RB {2\pi} \\
\th_l
= &2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \th_l'
  \; \mathrm {mod}\; \RB {2\pi}  \\
\V {b} \RB {\f}
= &\M {K}^\Adj \V {a} \RB {\f}
}

\textbf {Proposition 1}
Let \m {\f} be given.
Then, for any random instance of \m {\f},
\Disp {
\VNm {\V {b} \RB {\f} _{\SB{\mathcal {C}}}} _1
\leq \frac {2} {\pi} \log N 
}

To show this, introduce
\Disp {
\psi \RB {\f, n_H}
:=\RB {
   \f \; \mathrm {mod}\; \frac {2\pi} {N}
   + \RB {\frac {2 n_H} {N} + 1} \pi
} \;
\mathrm {mod}\; \RB {2\pi}
- \pi 
}
By using suitable remainder terms to estimate the Maclaurin series,
\Disp {
\frac {\Nm {\sin \RB {N \psi'/2}}} {\Nm {\sin \RB {\psi' /2}}}
\leq &B \RB {\psi'}
:= \frac {48} {\Nm {\psi'^2 -24} \Nm {\psi'}}, \\
}
Then, a simple verification shows
\Disp {
\VNm {\V {b} \RB {\f} _{\SB{\mathcal {C}}}} _1
\leq \frac {1} {N}
\VNm {
\RB {
   \sum_{n_H' =0}^{N -1}
      B \RB {\psi \RB {\f, n_H'}}
      \V {u} _{n_H'}
} _{\SB{\mathcal {C}}}
} _1
}
Or, if we carry out the integral and drop \m {s},
\Disp {
\VNm {\V {b} \RB {\f} _{\SB{\mathcal {C}}}} _1
\leq &\frac {1} {N} \D \frac {N} {2\pi} \D 2 \int_{\pi s/N}^{\pi} B \RB {\psi} ^2 d \psi \\
= &\frac {48} {N \pi^3}
\int _{s /N} ^1 \frac {1} {\RB {24/\pi^2 -x^2} ^2 x^2} dx \\
\leq &\frac {2} {\pi} \log N 
}

\textbf {Proposition 2}
The bound
\Disp {
\VNm {\M {g} _{\SB{\mathcal {C}}}} _1
\leq \frac {1} {3} L \RB {\log N_{H,t} + \log N_{H,r}} ^2
}
holds for probability \m {p}, with
\Disp {
1 -p
\leq 2 \exp \RB {- \frac {9L} {\pi}} 
}
This is proved by using Proposition 1 with triangle inequality, and bound the sample mean by Hoeffding inequality.

@@

Nevertheless, notice that if angles \m {\th_l} (respectively \m {\f_l}) are exactly the multiples of \m {2 \pi / N_{H,t}} (respectively \m {2 \pi / N_{H,r}}), then for some \m {S}-sparse \m {\V {d}'} and unitary \m {\M {U}},
\Disp {
&\VNm {\M {W} _B \M {W} _R \M {H} \M {F} _R \M {F} _B} _2 \notag \\
= &\VNm {
   \M {W} _B \M {W} _R \M {K} _r \M {U} \D
   \mathrm {diag} \SB {\mathrm {abs} \SB {\V {d}'}} \D
   \M {U} ^\dagger \M {K} _t ^\dagger \M {F} _R \M {F} _B} _2 \notag \\
= &\VNm {
   \M {W} _B \M {W} _R \M {K} _r \M {U}
   \R {\mathrm {abs} \SB {\V {d}'}}} _2 \D
   \VNm {\M {F} _B ^\dagger \M {F} _R ^\dagger \M {K} _t \M {U}
   \R {\mathrm {abs} \SB {\V {d}'}}} _2 \notag \\
\eqsim &\VNm {\M {G}} _2 \RB {1 +2\d_s} 
}
Thus, even we cannot make sure that \m {\M {P}} is \m {\d_s} RIP with respect to all possible \m {\V {g}}'s, at least \m {\M {P}} has RIP with respect to relevant values of \m {\V {g}} for which the channel is sparse.

@@

Finally, we shall show the proposed bound.
For simplicity, set \m {S = Ls^2}, thus \m {S =L \log N_h}.
And, for concreteness, suppose \m {\d_S \leq 1/8}.

\textbf {Theorem 9}
Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as above.
Then it holds that
\Disp {
\VNm {\V {d}} _2
\eqsim \mathcal {O} \RB {\R {L} \R {\log N_h}^3} 
}
for probability \m {p}, with
\Disp {
1 -p
\eqsim \mathcal {O} \RB {\mathsf {e} ^{-N_R \R {\d_s} /4}} 
}

To show this, by the definition of truncation, by \m {\ell_p} norm inequality, by Proposition 6,
\Disp {
\VNm {\M {P} _{\SB {\mathcal {AB}}}^\intercal \M {P} \V {d}} _2
\leq &\VNm {\M {P}^\intercal \M {P} \V {d}} _2 \\
\leq &\R {S} \VNm {\M {P}^\intercal \M {P} \V {d}} _\infty \\
\leq &2.83 \R {L} \log N_h
}
By \m {\ell_p}-norm inequality, by the definition of truncation, by Proposition 8, and by above,
\Disp {
\VNm {\V {d} _{\SB{\mathcal {A}}}} _1
\leq &\R {S} \VNm {\V {d} _{\SB{\mathcal {A}}}} _2 \\
\leq &\R {S} \VNm {\V {d} _{\SB{\mathcal {AB}}}} _2 \\
\leq &3.44 L \R {\log N_h}^3
+0.262 \VNm {\V {d} _{\SB{\mathcal {C}}}} _1
}
Then, substituting this and Proposition 2 above into Proposition 5, we get
\Disp {
\VNm {\V {d} _{\SB{\mathcal {C}}}} _1
\leq 5.12 L \RB {\log N_h}^2
}
Now Proposition 8 becomes
\Disp {
\VNm {\V {d} _{\SB{\mathcal {AB}}}} _2
\leq 3.44 \R {L} \log N_h + 1.35 \R {L} \R {\log N_h} ^3
}
Finally, by plugging \m {\VNm {\V {d} _{\SB{\mathcal {AB}}}} _2} and \m {\VNm {\V {d} _{\SB{\mathcal {C}}}} _1} into Proposition 7, we get
\Disp {
\VNm {\V {d}} _2
\leq 4.79 \R {L} \R {\log N_h}^3
}
Therefore, we set \m {\chi = \R {L} \R {\log N_h}^3}, so that \m {\VNm {\V {d}} _2 = \mathcal {O} \RB {\chi}}, as claimed.
The failure probability is taken from Proposition 3.

@@

First, complex numbers have to be recorded as the real and imaginary parts, to speed up calculation.
Let \m {\mathcal {R}} denote the representation of complex vectors and matrices by real vectors and matrices.
With definitions \m {\tilde {\V {y}} = \mathcal {R} \RB {\V {y}}},
\m {\tilde {\V {g}} = \mathcal {R} \RB {\V {g}}},
\m {\tilde {\M {P}} = \mathcal {R} \RB {\M {P}}},
\m {\tilde {\V {z}} = \mathcal {R} \RB {\V {z}}},
we have by construction
\Disp {
\V {\tilde {y}}
= \M {\tilde {P}} \V {\tilde {g}} +\V {\tilde {z}} 
}

@@

Alternatively, in our investigation, we cast DS into a basis pursuit denoising form, for suitable \m {\l} \cite {BoV04} as below.
\Disp {
\Hat {\V {g}}
\leftarrow \Min {\V {g}' \in \mathbb {C} ^{N_{H,t} N_{H,r}}}
\RB {\VNm {\V {g}'} _1 + \l \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty}
}
However, there is no simple way to determine the value of \m {\l} in advance.
We have tried \m {\l = N_{H,t} N_{H,r} / \g_{\mathrm {DS}}} in the simulation.

@@

We discuss the complexity of DS, Lasso, and OMP.
For DS, suppose a linear program has an \m {N} dimensional variable and \m {M} inequality constraints, then its complexity is \m {\mathcal {O} \RB {N^2 M}}, assuming the Dantzig simplex method is used \cite {BoV04}.
For our case, that would be \m {\mathcal {O} \RB {4 N_h ^2 \D 8 N_h} = \mathcal {O} \RB {N_h ^3}}.

Alternatively, suppose Newton method is used.
Here, we have self-concordance for linear program \cite {BoV04}.
Let \m {\V {g} _0} denote the starting value of \m {\V {g}'}, and \m {\V {g} ^{\star}} the the point of convergence.
Then the number of Newton steps, which we take to be the complexity, is bounded by \cite {BoV04}
\Disp {
N_{\mathrm {Newton}}
\propto \RB {\VNm {\V {g}_0 -\V {g} ^{\star}}_1
+ \log_2 \log_2 \frac {1} {\e}}
}

Assume that, at the start the iteration, the Moore–Penrose inverse is close to the initial value of \m {\V {g}_0}, namely
%
\Disp {
\V {g}_0
=\V {g}_{\mathrm {LS}}
= \RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {y} 
}
And suppose that, in view of restricted isometry, \m {\M {P}} has unity-normed, almost orthogonal columns, so that
\m {\M {P} ^\dagger \M {P} \approx I _{N_h}}
Moreover, assume that \m {\V {g} ^\star \approx \V {g}}.
Then we simply have
\Disp {
C_{\mathrm {DS}}
=\mathcal {O} \RB {N_h ^3} 
}

For OMP \cite {TrG07}, \m {C_{\mathrm {OMP}} =\mathcal {O} \RB {L \RB {\log N_h} ^2}}.

For Lasso, it is equivalent to a quadratically constrained quadratic program, and there is not always a closed form for its complexity.
However, Lasso and DS are equivalent in certain conditions \cite {AsR10}, and we may suppose here they have the same complexity.
Alternatively, an argument similar to the above one for DS is valid for Lasso.
Therefore we take \m {C_{\mathrm {Lasso}} =\mathcal {O} \RB {N_h ^3}}.

@@

\begin{thebibliography}{30}
\bibitem{RSM13}
T. S. Rappaport, S. Sun, R. Mayzus, H. Zhao, Y. Azar, K. Wang, G. N. Wong, J. K. Schulz, M. Samimi, and F. Gutierrez, “Millimeter wave mobile communications for 5g cellular: It will work!” \textit {IEEE access}, vol. 1, pp. 335–349, 2013.
\bibitem{RDD18}
M. Rani, S. B. Dhok, and R. Deshmukh, “A systematic review of compressive sensing: Concepts, implementations and applications,” \textit {IEEE Access}, vol. 6, pp. 4875–4894, 2018.
\bibitem{CaT05}
E. J. Candès and T. Tao, “Decoding by linear programming,” \textit {IEEE Transactions on Information Theory}, vol. 51, no. 12, p. 4203, 2005.
\bibitem{CaT07}
E. Candès and T. Tao, “The dantzig selector: Statistical estimation when p is much larger than n,” \textit {The annals of Statistics}, vol. 35, no. 6, pp. 2313–2351, 2007.
\bibitem{BDD08}
[6] R. Baraniuk, M. Davenport, R. DeVore, and M. Wakin, “A simple proof of the restricted isometry property for random matrices,” \textit {Constructive Approximation}, vol. 28, no. 3, pp. 253–263, 2008.
\bibitem{BHS10}
W. U. Bajwa, J. Haupt, A. M. Sayeed, and R. Nowak, “Compressed channel sensing: A new approach to estimating sparse multipath channels,” \textit {Proceedings of the IEEE}, vol. 98, no. 6, pp. 1058–1076, 2010.
\bibitem{BHR08}
W. U. Bajwa, J. Haupt, G. Raz, and R. Nowak, “Compressed channel sensing,” 2008 \textit {42nd Annual Conference on Information Sciences and Systems}, pp. 5–10, 2008.
\bibitem{AsR10}
